STRATEGIC SOCIAL LEARNING AND THE POPULATION DYNAMICS OF HUMAN BEHAVIOR: THE GAME OF GO

### 2018-10-17 4_prepare_manuscript/Rmarkdown/manuscript.Rmd
misc tweaks

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

<!-- n -->

@@

<!-- 44's correlation between performance and frequency -->
<!-- time trends in each -->

@@

<!-- variant frequency closely tracks relative performance -->

@@

<!-- takemiya's win rate -->

@@

<!-- model intercept of 53.2% -->
<!-- recent personal use predicts current use; 60% use outcome is 58.7% (OR 9.39) ceteris paribus -->
<!-- recent win rate predicts current use, OR of 2.77 -->
<!-- recent personal use and win rate interaction effect exists -->

@@

<!-- recent pop use of 60% means expected prob is 59%, OR 10.475 -->
<!-- recent pop use of 60% and +10% performance, its 61.4% -->

@@

<!-- social knowledge is 1.05x more important -->
<!-- varying effect sigma of 4.00 for player intecepts -->
<!-- varying effect sigma of 9.77 for player slopes on pop knowledge -->

@@

<!-- varying effect age trend -->

@@

<!-- national differences in sensitivities to social and individual info... -->

@@

<!-- n here same as above -->

@@

<!-- warmup and sampling interation counts -->
